Effectiveness of BNT162b2 booster doses in England: an observational study in OpenSAFELY-TPP

### 2022-03-28 manuscript/draft-manuscript.Rmd
v3 updates

cohortsummary <- read_csv(fs::path(output_dir_os, "cohortsummary.csv"))
matchsummary <- read_csv(fs::path(output_dir_os, "matchsummary.csv"))
matchsummary_treated <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 1L)
matchsummary_control <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 0L)
matchflowchart <- read_csv(fs::path(output_dir_os, "matchflowchart.csv"))
matchcoverage <- read_csv(fs::path(output_dir_os, "matchcoverage.csv"))
incidences <- read_csv(fs::path(output_dir_os, "none", "incidence_all.csv")) %>% mutate(events=events_1+events_0)
pfizerdurationweeks <- as.numeric(as.duration(study_dates$pfizerend_date - study_dates$pfizerstart_date +1) , "weeks")
```

@@

km <- 
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "km.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "km.csv")),
    read_csv(fs::path(output_dir_os, "cev", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "prior_covid_infection", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level = fct_inorder(subgroup_level),
    subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=15)),
    #model_name = fct_inorder(str_wrap(model_name, 15)),
  )

kmdiff <- km %>% 
  mutate(
    treated=(treated_descr=="Boosted")*1L
  ) %>%
  select(
    treatment, outcome , subgroup, 
    treated, surv, time, leadtime
  ) %>%
  pivot_wider(
    id_cols= c("treatment", "outcome", "subgroup", "time", "leadtime"),
    names_from=treated,
    names_prefix="surv_",
    values_from=surv
  ) %>%
  mutate(
    risk_1 = 1 - surv_1,
    risk_0 = 1 - surv_0,

    kmrr = risk_1 / risk_0,
    kmrd = risk_1 - risk_0,
    VErr = 1-kmrr,
    kmrrE = label_number(accuracy=0.01, scale=1)(kmrr),
    kmrdE = label_number(accuracy=0.01, scale=1000)(kmrd)
  )

km70 <- kmdiff %>% filter(leadtime==max(postbaselinecuts))
# 
# cmlinc <- read_csv(fs::path(output_dir_os, "cmlinc.csv")) %>%
#   mutate(
#     treatment_descr = fct_inorder(treatment_descr),
#     outcome_descr = fct_inorder(outcome_descr),
#     model_name = fct_inorder(str_wrap(model_name, 15)),
#     inc_CI_to = paste0(label_number(0.1, scale=1000)(1-survival.ul), " to ", label_number(0.1, scale=1000)(1-survival.ll))
#   )

# riskdiff <- read_csv(fs::path(output_dir_os, "riskdiff.csv")) %>%
#   mutate(
#     treatment_descr = fct_inorder(treatment_descr),
#     outcome_descr = fct_inorder(outcome_descr),
#     model_name = fct_inorder(str_wrap(model_name, 15)),
#     diff_CI_to = paste0(label_number(0.01, scale=1000)(diff.ll), " to ", label_number(0.01, scale=1000)(diff.ul))
#   )

hazards <- 
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "effects.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "effects.csv")),
    read_csv(fs::path(output_dir_os, "cev", "effects.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "prior_covid_infection", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(

@@

#cmlinc3 <- cmlinc %>% filter(model==3)
hazards3 <- hazards %>% filter(model==3)

riskdiff <- km %>% 
  group_by(treatment, treatment_descr, outcome, outcome_descr, outcome_descr_wrap, subgroup, subgroup_descr, subgroup_variable, subgroup_variable_descr, subgroup_level, subgroup_level_descr, time) %>%
  summarise(
    survdiff = diff(surv),
  ) %>% 
  mutate(
    survdiff_display = label_number(accuracy=0.1, scale=1000, big.mark =",")(survdiff),
    survdiff_inv_display = label_number(accuracy=0.1, scale=1000, big.mark =",")(-survdiff),
  ) %>%
  ungroup()
```

@@

<!-- https://www.england.nhs.uk/2021/09/nhs-begins-covid-19-booster-vaccination-campaign/ -->

<!-- 13 december 30-39 become eligible (https://www.england.nhs.uk/2021/12/nhs-to-roll-out-life-saving-booster-jab-to-people-aged-30-plus/) -->

<!-- 15 december everyone eligible https://www.england.nhs.uk/2021/12/nhs-booster-bookings-open-to-every-eligible-adult/ -->

@@

The supplementary materials provide further details of the matching process.
<!-- We excluded matched pairs from days in which fewer than 10% of eligible treated people were successfully. -->

@@

## Additional variables

@@

We used Cox models, stratified by recruitment day, NHS region, and brand of second vaccine dose, to estimate hazard ratios (HRs) comparing boosted with unboosted people, overall and separately for days 1-28 and 29-70. As we were not able to match on all potential confounders, these models included the following additional covariates: sex (male or female); English Index of Multiple Deprivation (IMD, grouped by quintile); ethnicity (Black, Mixed, South Asian, White, Other, as per the UK census); prior morbidity count (diabetes, BMI \> 40kg/m^2^, chronic heart disease, chronic kidney disease, chronic liver disease, chronic respiratory disease or severe asthma, chronic neurological disease); learning disabilities; severe mental illness; the number of SARS-CoV-2 tests in the 6 months prior to the study start date; elective in-hospital episode at the time of recruitment.A robust variance estimator was used to account for inclusion of some people in both the boosted and unboosted groups. Booster vaccine effectiveness was calculated as one minus the hazard ratio, expressed as a percentage.

@@

There were `r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="postest", fup_period=="All") %>% pull(events))` positive SARS-CoV-2 tests, 
`r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="covidadmitted", fup_period=="All") %>% pull(events))` COVID-19 hospital admissions, 
`r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="coviddeath", fup_period=="All") %>% pull(events))` COVID-19 deaths, 
and `r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="noncoviddeath", fup_period=="All") %>% pull(events))` non-COVID-19 deaths 
across `r label_number(1, big.mark=",")((filter(matchsummary, treatment=="pfizer") %>% pull(fup_years)) *365.25/7)` person-weeks of follow-up. 
The 10-week risk of positive SARS-CoV-2 test was `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` per 1000 in the boosted group 
and `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` in the unboosted group, 
representing a risk difference of `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=1000))` per 1000. 
For COVID-19 hospital admission, this was `r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
respectively (`r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events in the boosted group). 
For COVID-19 death it was `r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
(`r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events), 
and for non-COVID-19 death it was `r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
(`r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events) respectively  (Table 2).

@@

Amongst people classified as clinically extremely vulnerable estimated booster effectiveness was `r filter(overallhazards, outcome=="postest", treatment=="pfizer", subgroup=="cev-TRUE", model==3) %>% pull(ve_display)` for positive SARS-CoV-2 test, `r filter(overallhazards, outcome=="covidadmitted", treatment=="pfizer", subgroup=="cev-TRUE", model==3) %>% pull(ve_display)` for COVID-19 hospital admission, and `r filter(overallhazards, outcome=="coviddeath", treatment=="pfizer", subgroup=="cev-TRUE", model==3) %>% pull(ve_display)` for COVID-19 death. For people who not classified as clinically extremely vulnerable estimated booster effectiveness was slightly higher, at `r filter(overallhazards, outcome=="postest", treatment=="pfizer", subgroup=="cev-FALSE", model==3) %>% pull(ve_display)`, `r filter(overallhazards, outcome=="covidadmitted", treatment=="pfizer", subgroup=="cev-FALSE", model==3) %>% pull(ve_display)`, and `r filter(overallhazards, outcome=="coviddeath", treatment=="pfizer", subgroup=="cev-FALSE", model==3) %>% pull(ve_display)`, respectively. Estimated booster effectiveness for non-COVID-19 death was similar for those who were and were not classified as clinically extremely vulnerable: `r filter(overallhazards, outcome=="noncoviddeath", treatment=="pfizer", subgroup=="cev-TRUE", model==3) %>% pull(ve_display)` and `r filter(overallhazards, outcome=="noncoviddeath", treatment=="pfizer", subgroup=="cev-FALSE", model==3) %>% pull(ve_display)` respectively.

@@

incidences %>%
  left_join(kmdiff %>% filter(time = postbaselinecuts[-1] -1)) %>%
  filter(
    fup_period == "All",
    outcome %in% outcomes,
    treatment == "pfizer"
  ) %>%
  select(
    #treatment_descr, 
    outcome_descr,
    #fup_period,
    q_1,
    risk_1,
    q_0, 
    risk_0,
    kmrrE,
    kmrdE
    #rrECI
  ) %>%
  mutate(
    risk_1=if_else(risk_1<0.001, "<0.001", label_number(0.001)(risk_1)),
    risk_0=if_else(risk_0<0.001, "<0.001", label_number(0.001)(risk_0)),
  ) %>%
  gt(
   #groupname_col = c("treatment_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    outcome_descr = "Outcome",
    #fup_period = "Days since booster",
    q_0 = "Events / person-years",
    q_1   = "Events / person-years",

>>>>

cohortsummary <- read_csv(fs::path(output_dir_os, "cohortsummary.csv"))
matchsummary <- read_csv(fs::path(output_dir_os, "matchsummary.csv"))
matchsummary_treated <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 1L)
matchsummary_control <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 0L)
matchflowchart <- read_csv(fs::path(output_dir_os, "matchflowchart.csv"))
matchcoverage <- read_csv(fs::path(output_dir_os, "matchcoverage.csv"))
incidence_all <- read_csv(fs::path(output_dir_os, "none", "incidence_all.csv")) %>% mutate(events=events_1+events_0)
pfizerdurationweeks <- as.numeric(as.duration(study_dates$pfizerend_date - study_dates$pfizerstart_date +1) , "weeks")
```

@@

km <- 
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "km.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "km.csv")),
    read_csv(fs::path(output_dir_os, "cev", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    #read_csv(fs::path(output_dir_os, "prior_covid_infection", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level = fct_inorder(subgroup_level),
    subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=15)),
    #model_name = fct_inorder(str_wrap(model_name, 15)),
    treated = (treated_descr=="Boosted")*1L
  ) %>%
  group_by(treatment, treated_descr, outcome, subgroup) %>%
  mutate(
    cml.risk = cumsum(n.risk),
    cml.event = cumsum(replace_na(n.event, 0)),
  )

groupvariables <- c("treatment", "treatment_descr", "outcome", "outcome_descr", "outcome_descr_wrap", "subgroup", "subgroup_descr", "subgroup_level", "subgroup_level_descr")

km_incidence <-
  km %>%
  mutate(
    n.atrisk = n.risk,
    cml.atrisk = cumsum(replace_na(n.atrisk, 0)),
    cml.event = cumsum(replace_na(n.event, 0)),
    cml.censor = cumsum(replace_na(n.censor, 0)),
    rate = n.event/n.atrisk,
    cml.rate = cml.event / cml.atrisk,
    risk = 1 - surv,
  ) %>%
  select(
    treated,
    all_of(groupvariables),
    time, interval,
    surv, risk, n.atrisk, n.event, n.censor, rate, cml.atrisk, cml.event, cml.censor, cml.rate
  )

kmconstrast <- function(data, cuts=NULL){

  if(is.null(cuts)){cuts <- unique(data$time)}

  data %>%
    filter(time!=0) %>%
    mutate(
      period_start = cut(time, cuts, right=TRUE, label=cuts[-length(cuts)]),
      period_end = cut(time, cuts, right=TRUE, label=cuts[-1]),
      period = cut(time, cuts, right=TRUE, label=paste0(cuts[-length(cuts)]+1, " - ", cuts[-1]))
    ) %>%
    group_by(across(all_of(groupvariables))) %>%
    group_by(
      treated, period_start, period_end, period,
      .add = TRUE
    ) %>%
    summarise(
      interval = last(time) - first(time) + 1,
      time=last(time),
      cml.atrisk = last(cml.atrisk),
      cml.event = last(cml.event),
      cml.censor = last(cml.censor),
      cml.rate = last(cml.rate),
      persontime = sum(n.atrisk),
      n.atrisk = first(n.atrisk),
      n.event = sum(n.event, na.rm=TRUE),
      n.censor = sum(n.censor, na.rm=TRUE),
      surv = last(surv),
      risk = last(risk),
      rate = n.event/persontime,
    ) %>%
    pivot_wider(
      id_cols= c(groupvariables, "period_start", "period_end", "period",  "interval", "time"),
      names_from=treated,
      names_glue="{.value}_{treated}",
      values_from=c(surv, risk, n.atrisk, n.event, n.censor, rate, cml.atrisk, cml.event, cml.censor, cml.rate)
    ) %>%
    mutate(
      kmrr = risk_1 / risk_0,
      kmrd = risk_1 - risk_0,
      irr = rate_1 / rate_0,
      ird = rate_1 - rate_0,
      cmlirr = cml.rate_1 / cml.rate_0,
      cmlird = cml.rate_1 - cml.rate_0
    ) %>%
    mutate(
      kmrd_display = label_number(accuracy=0.1, scale=1000, big.mark =",")(kmrd),
      kmrd_inv_display = label_number(accuracy=0.1, scale=1000, big.mark =",")(-kmrd),
    ) %>%
    mutate(
      cml.events = cml.event_0 + cml.events_1,
      cml.atrisk = cml.atrisk_0 + cml.atrisk_1
    )
}

kmtreated_daily <- kmconstrast(km_incidence)
kmtreated_cuts <- kmconstrast(km_incidence, postbaselinecuts)
kmtreated_overall <- kmconstrast(km_incidence, c(0,last(postbaselinecuts)))

km70 <- kmtreated_daily %>% filter(time==max(postbaselinecuts))

# 
# incidence <- 
#   bind_rows(
#     read_csv(fs::path(output_dir_os, "none", "incidence.csv")),
#     read_csv(fs::path(output_dir_os, "vax12_type", "incidence.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
#     #read_csv(fs::path(output_dir_os, "cev", "incidence.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
#     #read_csv(fs::path(output_dir_os, "age65plus", "incidence.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
#     #read_csv(fs::path(output_dir_os, "prior_covid_infection", "incidence.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
#   ) %>%
#   filter(
#     outcome %in% outcomes
#   ) %>%
#   mutate(
#     subgroup_descr = fct_inorder(subgroup_descr),
#     subgroup_level = fct_inorder(subgroup_level),
#     #subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
#     treatment_descr = fct_inorder(treatment_descr),
#     outcome_descr = fct_inorder(outcome_descr),
#     outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=15)),
#   )

hazards <- 
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "effects.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "effects.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "cev", "effects.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "prior_covid_infection", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(

@@

hazards3 <- hazards %>% filter(model==3)

@@

<!-- https://www.england.nhs.uk/2021/09/nhs-begins-covid-19-booster-vaccination-campaign/ -->
<!-- 13 december 30-39 become eligible (https://www.england.nhs.uk/2021/12/nhs-to-roll-out-life-saving-booster-jab-to-people-aged-30-plus/) -->
<!-- 15 december everyone eligible https://www.england.nhs.uk/2021/12/nhs-booster-bookings-open-to-every-eligible-adult/ -->

@@

The supplementary materials provide further details of the matching process.

@@

@@

We used Cox models, stratified by recruitment day, NHS region, and brand of second vaccine dose, to estimate hazard ratios (HRs) comparing boosted with unboosted people, overall and separately for days 1-28 and 29-70, and also for days 1-7, 8-14, 15-28, 29-42, and 43-70. As we were not able to match on all potential confounders, these models included the following additional covariates: sex (male or female); English Index of Multiple Deprivation (IMD, grouped by quintile); ethnicity (Black, Mixed, South Asian, White, Other, as per the UK census); prior morbidity count (diabetes, BMI \> 40kg/m^2^, chronic heart disease, chronic kidney disease, chronic liver disease, chronic respiratory disease or severe asthma, chronic neurological disease); learning disabilities; severe mental illness; the number of SARS-CoV-2 tests in the 6 months prior to the study start date; elective in-hospital episode at the time of recruitment.A robust variance estimator was used to account for inclusion of some people in both the boosted and unboosted groups. Booster vaccine effectiveness was calculated as one minus the hazard ratio, expressed as a percentage.

@@

There were `r label_number(1, big.mark=",")(filter(km70, treatment=="pfizer", outcome=="postest") %>% pull(cml.events))` positive SARS-CoV-2 tests,
`r label_number(1, big.mark=",")(filter(km70, treatment=="pfizer", outcome=="covidadmitted") %>% pull(cml.events))` COVID-19 hospital admissions, 
`r label_number(1, big.mark=",")(filter(km70, treatment=="pfizer", outcome=="coviddeath") %>% pull(cml.event))` COVID-19 deaths, 
and `r label_number(1, big.mark=",")(filter(km70, treatment=="pfizer", outcome=="noncoviddeath") %>% pull(cml.events))` non-COVID-19 deaths 
across `r label_number(1, big.mark=",")((filter(km70, treatment=="pfizer", outcome="coviddeath") %>% pull(cml.atrisk)) /7)` person-weeks of follow-up. 
The 10-week risk of positive SARS-CoV-2 test was `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` per 1000 in the boosted group 
and `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` in the unboosted group, 
representing a risk difference of `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=1000))` per 1000. 
For COVID-19 hospital admission, this was `r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
respectively (`r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events in the boosted group). 
For COVID-19 death it was `r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
(`r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events), 
and for non-COVID-19 death it was `r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
(`r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events) respectively  (Table 2).

@@

Amongst people classified as clinically extremely vulnerable estimated booster effectiveness was `r filter(overallhazards, outcome=="postest", treatment=="pfizer", subgroup=="cev-TRUE", model==3) %>% pull(ve_display)` for positive SARS-CoV-2 test, `r filter(overallhazards, outcome=="covidadmitted", treatment=="pfizer", subgroup=="cev-TRUE", model==3) %>% pull(ve_display)` for COVID-19 hospital admission, and `r filter(overallhazards, outcome=="coviddeath", treatment=="pfizer", subgroup=="cev-TRUE", model==3) %>% pull(ve_display)` for COVID-19 death. For people who were not classified as clinically extremely vulnerable estimated booster effectiveness was slightly higher at `r filter(overallhazards, outcome=="postest", treatment=="pfizer", subgroup=="cev-FALSE", model==3) %>% pull(ve_display)`, `r filter(overallhazards, outcome=="covidadmitted", treatment=="pfizer", subgroup=="cev-FALSE", model==3) %>% pull(ve_display)`, and `r filter(overallhazards, outcome=="coviddeath", treatment=="pfizer", subgroup=="cev-FALSE", model==3) %>% pull(ve_display)`, respectively. Estimated booster effectiveness for non-COVID-19 death was similar for those who were and were not classified as clinically extremely vulnerable: `r filter(overallhazards, outcome=="noncoviddeath", treatment=="pfizer", subgroup=="cev-TRUE", model==3) %>% pull(ve_display)` and `r filter(overallhazards, outcome=="noncoviddeath", treatment=="pfizer", subgroup=="cev-FALSE", model==3) %>% pull(ve_display)` respectively.

@@

incidence_table <- 
  incidence %>%
  left_join(
    kmdiff %>% filter(time == postbaselinecuts[-1] -1),
    by = c("treatment", "outcome", "subgroup", )
  ) %>%
  filter(
    #fup_period == "All",
    outcome %in% outcomes,
    treatment == "pfizer"
  ) %>%
  select(
    #treatment_descr, 
    outcome_descr,
    #fup_period,
    q_1,
    risk_1,
    q_0, 
    risk_0,
    kmrrE,
    kmrdE
    #rrECI
  ) %>%
  mutate(
    risk_1=if_else(risk_1<0.001, "<0.001", label_number(0.001)(risk_1)),
    risk_0=if_else(risk_0<0.001, "<0.001", label_number(0.001)(risk_0)),
  )

  gt(
    incidence_table
   #groupname_col = c("treatment_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    outcome_descr = "Outcome",
    #fup_period = "Days since booster",
    q_0 = "Events / person-years",
    q_1   = "Events / person-years",
